---
title: "2016-0509 MSDS 6304-401 9.5 Perparing Financial Data"
author: "Bill Kerneckel"
date: "July 13, 2016"
output:
  html_document:
    keep_md: yes
---

<br>

#### Assignment


Half of you will be assigned to find a series that is less volatile than the S&P 500, the other half a series that is more volatile.

1. Download the data.
2. Calculate log returns.
3. Calculate volatility measure.
4. Calculate volatility over entire length of series for various three different decay factors.
5. Plot the results, overlaying the volatility curves on the data, just as was done in the S&P example.9


Deliverable

1. Upload the Markdown file containing your code, analysis, and discussion to GitHub. Post a link to the Markdown file in the space below.
2. The markdown document should have code for entering the data, calculating log returns, calculating volatility measure, and calculating       volatility for the entire series using three different decay factors.
3. Also needs to have code for a plot (and the plot itself) with the data and volatility overlaid.
4. The discussion board will talk about the differences in the volatility plots for different stocks.

****************************

#### Setting your working directory

In order for the analysis of financial data you must set your working directory to the following:

```{r}
setwd("/Users/wkerneck/desktop/9.5 Perparing Financial Data/")
```

****************************

#### Libraries needed to perform financial analysis

```{r}
library(tseries)
```

****************************

#### Functions needed to perform financial analysis

```{r}
SNPdata <- get.hist.quote('^gspc',quote="Close")
SNPret <- log(lag(SNPdata)) - log(SNPdata)
SNPvol <- sd(SNPret) * sqrt(250) * 100

Vol <- function(d, logrets) {
  var = 0
  lam = 0
  varlist <- c()
  for (r in logrets) {
    lam = lam*(1 - 1/d) + 1
  var = (1 - 1/lam) * var + (1/lam) * r^2
    varlist <- c(varlist, var)
  }
  sqrt(varlist)}
```

****************************

